---
title: "Reviewer_comments"
author: "Iza"
date: "2023-10-10"
output: html_document
---

Load packages

```{r}
library(tidyverse)
library(readr)
library(readxl)
library(clusterProfiler)

```

Load the mirtarbase table
```{r}
miRTarBase_MTI <- read_excel("ref/miRTarBase_MTI.xlsx")
```

Load the mirtarbase table
```{r}
miRTarBase_MTI <- read_excel("ref/miRTarBase_MTI.xlsx")
```

filter only human
```{r}
miRTarBase_MTI <-miRTarBase_MTI %>% filter(`Species (miRNA)` == "Homo sapiens")
```

filter support type not weak

```{r}
miRTarBase_MTI_notweak <-miRTarBase_MTI %>% filter(`Support Type` == "Functional MTI")
```

Load c2

```{r}
c2_full <-read.gmt("ref/c2.cp.v2023.1.Hs.symbols.gmt.txt")
```


Get the tables for the specific microRNAs

1274a
```{r}
"hsa-miR-1274a"

table_1274a <-miRTarBase_MTI %>% filter(miRNA == "hsa-miR-1274a")

```

193a-5p

```{r}
"hsa-miR-193a-5p"

table_193a <-miRTarBase_MTI %>% filter(miRNA == "hsa-miR-193a-5p")

```

28-3p
```{r}
"hsa-miR-28-3p"

table_28_3p <-miRTarBase_MTI %>% filter(miRNA == "hsa-miR-28-3p")

```

30a-3p

```{r}
"hsa-miR-30a-3p"

table_30a_3p <-miRTarBase_MTI %>% filter(miRNA == "hsa-miR-30a-3p")

```

145
```{r}
"hsa-miR-145-3p"
"hsa-miR-145-5p"

table_145 <-miRTarBase_MTI %>% filter(miRNA %in% c("hsa-miR-145-3p", "hsa-miR-145-5p"))

```

19b
```{r}
"hsa-miR-19b-3p"
"hsa-miR-19b-5p"

table_19b <-miRTarBase_MTI %>% filter(miRNA %in% c("hsa-miR-19b-3p", "hsa-miR-19b-5p"))

```


143
```{r}
"hsa-miR-143-3p"
"hsa-miR-143-5p"

table_143 <-miRTarBase_MTI %>% filter(miRNA %in% c("hsa-miR-143-3p", "hsa-miR-143-5p"))
```

Total number of miRNA: 10

Enrich 1000 random miRNA

Sample 10 random miRNA from the mirTarBase Functional MTI table and enrich them separately saving on a list

```{r}
enrichment_results_list <- list()
num_random_samples <- 1000
set.seed(777)

for (i in 1:num_random_samples) {
  random_sample_miRNAs <- sample(miRTarBase_MTI$miRNA, size =
                                   1,
                                 replace = TRUE)
  random_sample_MTI <- miRTarBase_MTI[miRTarBase_MTI$miRNA %in%
                                        random_sample_miRNAs, ]
  target_genes <- unique(random_sample_MTI$`Target Gene`)
  random_enrichment <- enricher(gene = target_genes, TERM2GENE = c2_full,pvalueCutoff = 0.05, pAdjustMethod = "BH")
  enrichment_results_list[[i]] <- as.data.frame(random_enrichment)
}


```

Count the times each pathway appears on the 1000 lists and save it on a data.frame
```{r}
pathway_counts <- list()

for (i in 1:1000) {
  current_iteration <- enrichment_results_list[[i]]$ID
  for (pathway in current_iteration) {
    if (pathway %in% names(pathway_counts)) {
      pathway_counts[[pathway]] <- pathway_counts[[pathway]] + 1
    } else {
      pathway_counts[[pathway]] <- 1
    }
  }
}

pathway_counts_df <- data.frame(Pathway = names(pathway_counts), Count = unlist(pathway_counts))

```

From our selected pathways

WP_EGFEGFR_SIGNALING_PATHWAY
WP_MAPK_SIGNALING_PATHWAY
KEGG_MAPK_SIGNALING_PATHWAY
WP_MAPK_CASCADE
WP_TGFBETA_SIGNALING_PATHWAY
WP_DNA_DAMAGE_RESPONSE_ONLY_ATM_DEPENDENT
REACTOME_INTRACELLULAR_SIGNALING_BY_SECOND_MESSENGERS

Only the MAPK associated pathways (WP_MAPK_SIGNALING_PATHWAY, KEGG_MAPK_SIGNALING_PATHWAY, WP_MAPK_CASCADE) were not present in over 10% of the random microRNAs enrichment so we decided, following the reviewer comments to focus the discussion on those pathways










